The pollination trade-off

### 2018-02-28 publication/supp_info.Rmd
Improve best random effect contingency table
This time it includes more model metrics and the sample size (n models)

summ <- glanced_random %>%
  filter(var_trans == "log") %>%
  group_by(pollen_category, scale, var_trans, model) %>%
  mutate(delta_AIC = AIC - min(AIC)) %>%
  group_by(pollen_category, scale, var_trans, random_effect) %>%
  summarise(AIC_50 = median(delta_AIC), 
            AIC_05 = quantile(delta_AIC, 0.05),
            AIC_95 = quantile(delta_AIC, 0.95)) %>% 
  mutate_if(is.numeric, round, digits = 1) %>% 
  mutate(delta_AIC = paste0(AIC_50, " [", AIC_05, ", ", AIC_95, "]")) %>%
  group_by() %>%
  humanize(random_effects = random_effects) %>%
  arrange(pollen_category, scale, random_name) %>%
  rename(`pollen category` = pollen_category, 
         `random structure` = random_name)

contingency_table <- summ %>%
  # select(-var_trans) %>%
  ftable(row.vars = 10, col.vars = c(1, 2))

>>>>

summ <- glanced_random %>%
  filter(var_trans == "log") %>%
  group_by(pollen_category, scale, var_trans, model) %>%
  mutate(delta_AIC = AIC - min(AIC)) %>%
  group_by(pollen_category, scale, var_trans, random_effect) %>%
  summarise(AIC_50 = median(delta_AIC), 
            AIC_05 = quantile(delta_AIC, 0.05),
            AIC_95 = quantile(delta_AIC, 0.95), 
            n = n()) %>% 
  group_by() %>%
  select(-var_trans) %>%
  right_join(expand.grid(pollen_category = unique(.$pollen_category),
                        scale = unique(.$scale),
                        random_effect = unique(.$random_effect))) %>% 
  mutate_if(is.numeric, round, digits = 1) %>% 
  mutate(delta_AIC = paste0(AIC_50, " [", AIC_05, ", ", AIC_95, "], n = ", n), 
         delta_AIC = if_else(grepl("NA", delta_AIC), "---", delta_AIC)) %>%
  group_by() %>%
  humanize(random_effects = random_effects) %>%
  arrange(pollen_category, random_name, scale) %>%
  rename(`pollen category` = pollen_category, 
         `random structure` = random_name)

contingency_table <- xtabs( ~ `random structure` + `scale` + `pollen category` , data = summ) %>% ftable()

# contingency_table <- summ %>%
  # ftable.formula(`random structure` ~ `scale` + `pollen category`)
